Questionnaire to Developers

### 2020-05-13 StateOfPractice/Ao-Notes/Questionnaire.tex
hard wrap to 80 width
Update questionnaire

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{xspace}
\usepackage{fullpage}
\usepackage{hyperref}

@@

\title{Template for Grading Scientific Computing Software} 
\author{Spencer Smith, Adam Lazzarato, Yue Sun, Zheng Zeng,\\ Vasudha Kapil and Jacques Carette}
\date{\today}

\maketitle
\include{GradingTemplate}

>>>>

\usepackage{natbib}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{xspace}
\usepackage{fullpage}
\usepackage{hyperref}

@@

\maketitle

\section{Information about the developers and users}\citep{Jegatheesan2016}
\begin{enumerate}
\item Interviewees' current position/title? degrees?
\item Interviewees' contribution to/relationship with the software?
\item Length of time the interviewee has been involved with this software?
\item How large is the development group?
\item What is the typical background of a developer?
\item How large is the user group?
\item What is the typical background of a user?
\end{enumerate}

\section{Information about the software}

\ad{I drafted another version without considering our measurements}

\noindent\ad{3 aspects: dev process, software quality, user feedback}

\begin{enumerate}
\item Currently, what is the biggest obstacle against your development process?
\item In order to solve this problem, is there any improvement needed for your
development process?
\item In the past, is there any major obstacle to your development process that
has been solved? How did you solve it?
\item What is your project management process? Do you think improve this process
can tackle the current problem?
\item What is your documentation process? Do you think improve this process can
tackle the current problem?
\item Can you name several software qualities that are the most important to
this project?
\item Is any of them hard to be achieved? If yes, what methods have considered
or practiced to improve the situation? If practiced, does it work?
\item Do you think the users can understand your software well? Has there been
any problem to use this software?
\item Do you think the current documentation can clearly convey all necessary
knowledge to the users? If yes, how did you successfully achieve it? If no, what
improvements are needed?
\end{enumerate}

\newpage

\bibliographystyle {plainnat}
\bibliography {../../CommonFiles/ResearchProposal}
